Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
fixing figs sizes
fixing floats, grr

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test2}
\caption{Acoustic scene similarity retrieval (ASSR) in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for MFCCs and scattering with logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_1}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test1}
\caption{Acoustic scene similarity retrieval (ASSR) in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering coefficients, with and without logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_2}
\end{center}
\end{figure}

\subsection{Acoustic Scene Classification}
We report experiments on acoustic scene classification (ASC), following the original methodology of the DCASE 2013 challenge, and extend our approach to the its 2016 edition.

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\columnwidth]{gfx/unsupervised_test2}
\caption{Acoustic scene similarity retrieval (ASSR) in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for MFCCs and scattering with logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_1}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\columnwidth]{gfx/unsupervised_test1}
\caption{Acoustic scene similarity retrieval (ASSR) in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering coefficients, with and without logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_2}
\end{center}
\end{figure}

\subsection{Acoustic Scene Classification}

We report experiments on acoustic scene classification (ASC), following the original methodology of the DCASE 2013 challenge, and extend our approach to the its 2016 edition.
